### 2018-05-06 papers/synth/experiments.tex
z3 tabbel

    plos1-dia[3/4C]& 0.0292&$\infty$& 0.0255 &$\infty$& 0.1005      & $\infty$ & 0.0843&$\infty$& 0.0492 & 0.0\\\hline
    plos2-dia [4C] & 0.0414& 0      & 0.0407 & 0      & 2.327       & 1N 9PE   & 1.333 & 1 node & 0.042  & 0 \\\hline
    mukund[3/4C]  & 185.06 & 4N 8E  & 0.3773 & 0.0    & !13.92/1.553& 0.0      & 2.062 & 0.0    & 0.230  & 0.0 \\\hline
    node4[-]      & 16.70  & 0.0    & 16.472 & 0.0    & 7.011       & $\infty$ & 5.085 &$\infty$& 2.194  & 0.0\\\hline
    yeast-graph   & 0.0    & 0.0    & 0.0    & 0.00   & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0 \\\hline
    mukund-comp   & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline
  \end{tabular}
  \caption{Run-times for searching for models (in secs). \#C  stands for minimum changes.
  Time is reported in seconds.}
  \label{tab:qf-graph}
\end{table}
%[M=8, N=2, Q=2]    
% n/A n/A activeN == UNSAT adding edge == UNSAT activeE == UNSAT presenceE == UNSAT

>>>>

    plos1-dia[3/4C]& 0.0292&$\infty$& 0.0255 &$\infty$& 0.1005      & $\infty$ & 0.0843&$\infty$& 0.0492 & 0.0\\\hline
    plos2-dia [4C] & 0.0414& 0      & 0.0407 & 0      & 2.327       & 1N 9PE   & 1.333 & 1 node & 0.042  & 0 \\\hline
    mukund[3/4C]  & 185.06 & 4N 8E  & 0.3773 & 0.0    & !13.92/1.553& 0.0      & 2.062 & 0.0    & 0.230  & 0.0 \\\hline
    node4[-]      & 16.70  & 0.0    & 16.472 & 0.0    & 7.011       & $\infty$ & 5.085 &$\infty$& 2.194  & 0.0\\\hline
    yeast-graph   & 0.0    & 0.0    & 0.0    & 0.00   & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0 \\\hline
    mukund-comp   & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline
  \end{tabular}
  \caption{Run-times for searching for models (in secs). \#C  stands for minimum changes.
  Time is reported in seconds.}
  \label{tab:qf-graph}
\end{table}

    plos1-dia & 0.041&$\infty$& 0.320 &$\infty$& 0.225 & $\infty$ & 0.33&$\infty$& 3.74 & del: . 1 edge, 1 edge bit 1 node, 1 act each add: 1 edge bit 1 node bit\\\hline
    plos2-dia & 3.97 & 0 &  2.647 & 0  & 5.941 & 0 & 5.680 & 0 & 3.56 & 0 \\\hline
    mukund  & 3.483 & 1 edge  & 4.379 & 5 edge bits  & 6.340[-] / 29.980 & 2 edge, 10 edge bits  & 10.4052[-] & [-] & 3.650  &  del : 1 edge, 2 edge bit, 1 active node. add:1 edge 4 edge bit 4 node bit, 2 act \\\hline
    node4  & 4.1502  & 1 edge  & 10.562  & 12 mol & 3.401  & $\infty$ & 4.760 &$\infty$&  5.05  & del: 2 edge, 2 act, 1 node and 1 act. add: 12 node, 8 edge, 1 edge bits \\\hline
    yeast-graph & 40.8728  & 1 edge  &   timeout  & N/A   & 1313.91  & 1 edge  & 517.619   & 1 edge    & 380.43  &  del: 1 edge, 2 node, 2 act bits each. add: 2 edge, 12 mol, 7 node bits \\\hline
    mukund-comp   & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline
  \end{tabular}
  \caption{Run-times for searching for Z3 models (in secs). \#C  stands for minimum changes.
  Time is reported in seconds.}
  \label{tab:z3-qf-graph}
\end{table}

%[M=8, N=2, Q=2]    
% n/A n/A activeN == UNSAT adding edge == UNSAT activeE == UNSAT presenceE == UNSAT
